### 2022-03-31 manuscript/thesis.Rnw
revisions to section 1

\usepackage{framed}
\usepackage{changepage}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
\usepackage{graphicx}
\usepackage{subfig}
% Standard, old-style thesis
\usepackage{isutraditional}   
\chaptertitle
% Old-style, thesis numbering down to subsubsection
\alternate
\nochap
\usepackage{rotating}
% Bibliography without numbers or labels
\usepackage{natbib}
% Use the following line if you want square brackets and numbering system
%\usepackage[square, numbers]{natbib}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}
\makeatletter

@@

\usepackage{chapterbib}
%\renewcommand\bibsection{\section*{\ref name}}
%\renewcommand\bibsection{\section*}
\renewcommand{\bibsection}{\section{References}}

@@

\usepackage{amssymb}
\usepackage[intoc, english]{nomencl}

\begin{document}
\SweaveOpts{concordance=TRUE}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
%\begin{singlespace}
\def\@makechapterheada{\vspace*{-2cm}\titlepage} % in order to reduce the space between margin and heading in titlepage
\include{Preface/titlepage}
%\end{singlespace}

@@

\section{Introduction}
Predicting the outcomes of prospective events is the object of much scientific
inquiry and the basis for many decisions both public and private. Because 
predictions of the future can almost never be precise, it is usually desirable
that a level of uncertainty be attached to any prediction. In recent years, it
has become increasingly desirable that forecasts be probabilistic in order to 
account for uncertainty in predicted quantities or events 
\cite{gneiting2014probabilistic}. Specific problems for 
which probabilistic forecasting is used include weather forecasting
\cite{baran2018combining}, economics \cite{groen2013real} and disease outbreaks
\cite{yamana2016superensemble}.

A probabilistic forecast is a forecast to which probabilities are assigned to 
various possible outcomes. There are a number of ways whereby probabilities or 
uncertainty may be represented. A common representation is either a continuous 
or
discrete parametric distribution, given as a probability density/mass function 
(pdf/pmf). Much of the literature 
on calibration, sharpness and scoring of a forecast pertains to parametric 
distribution forecasts
\cite{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
Other common representations include samples \cite{krueger2016probabilistic}, 
discretized bins \cite{mcgowan2019collaborative}
and quantile or interval type forecasts \cite{taylor2021evaluating} 
\cite{bracher2021evaluating}. Each representation may be more or less 
appropriate than the others for a given problem but knowing how to interpret, 
score and contruct ensemble forecasts for a selected representation is essential
when multiple teams collaborate in the same forecasting project.

Two collaborative projects on forecasting disease outbreaks for which many 
separate forecasts 
are used include the United States Centers for Disease Control (CDC) hosted
annual competition for forecasting influenza \cite{cdcflusight}
and the COVID-19 Forecast Hub which has 
continuously operated since the start of the COVID-19 pandemic in the US in 
early 2020 \cite{Cramer2021-hub-dataset}.

\subsection{CDC Influenza Like Illness}

Since the 2013-14 flu season, the CDC has hosted an annual competition for 
predicting the timing, peak and intensity of the year's flu season. Forecasts
for the different targets also include predictions for one, two, three and 
four weeks ahead of the prediction time. National flu data is provided weekly 
to outside academic teams who use that data to construct forecasts using 
whatever methods they choose. Historically, the forecast predictions must be 
submitted 
in a discretized bin
format. During previous flu seasons the binning scheme was on a bounded numeric 
scale and the 
prediction of a specific target was a set of probabilities assigned to each bin
\cite{mcgowan2019collaborative}.
These forecasts are then evaluated against actual flu activity, and at 
the end of the season a winning team is declared \cite{cdcflusight}.

This competition has provided the CDC, competing teams and other interested
parties a chance to collaborate and improve forecasting each season. One 
proposed way to enhance prediction has been to aggregate the various teams'
forecasts into a multi-model ensemble forecast 
\cite{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy}.

A multi-model ensemble forecast is a combination of several component forecast 
models into one model which often yields better predicting power than the 
individual models \cite{cramer2021evaluation}. Such an ensemble made from 
multiple influenza competition forecasts did in fact outperform the individual 
component models \cite{reich2019accuracy}.
In the COVID-19 Forecast Hub, construction of ensemble forecasts is a main
priority.

\subsection{COVID-19 Forecast Hub}
In March 2020, at the onset of the COVID-19 pandemic, the COVID-19 Forecast Hub
was founded. Borrowing on work and 
ideas from the CDC influenza competition, the Forecast Hub is a central site in 
which dozens of academic teams collaborate to forecast the ongoing COVID-19 
pandemic.
Every week relevant
pandemic data is provided to these teams who build probabilistic models for 
their use in
forecasting cases, hospitalizations and deaths due to COVID-19. Forecasts are 
made on the US county,
state and national level with predictions for days, weeks and months ahead.
These forecasts are combined into a single ensemble forecast. The model data,
forecasts and the ensemble are passed along to the CDC for its use in official
communication \cite{Cramer2021-hub-dataset}. See Figure \ref{fig:cdcoff}.

Though similar to the forecasting in the influenza competition, the format of 
the COVID-19 Forecast Hub has some key distinctions. For one this project has
been operating continuously since it first began, so forecasts have been made
for over 100 straight weeks. 
As well due to the initial lack of understanding of the COVID-19 virus and the 
time 
pressure of
creating forecasts, rather than requesting forecasts as binned probabilities
the forecasts are requested as the predictive median and 
predictive intervals for various nominal levels depending on the target to be
predicted \cite{bracher2021evaluating}. Collecting forecasts in this quantile
or interval type format brings with it differences in how to score, construct 
ensemble
models and store the forecasts among other differences.

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.12]{Images/8_30_21_cvd_deaths.jpeg}}
\caption[Official CDC COVID-19 deaths report August 2021]{This image, 
published on cdc.gov as official public communication 
by the CDC, shows forecast models for national new weekly deaths due to COVID-19 
in the top row and cumulative deaths on the bottom row. The plots in the left 
column show prediction intervals from multiple teams whereas the plots on the 
right show the intervals for an ensemble forecast model.}
\label{fig:cdcoff}
\end{figure}

\subsection{}
In the context of collaborative forecasting like that of the CDC flu competition
or the COVID-19 Forecast Hub, discretized bins and quantile forecasts have 
proven useful and effective. Yet both types come with their drawbacks. Data 
storage for instance might be a concern if many bins are used for forecasting. 
And scoring methods are limited if forecasts are made of prediction intervals.

In this paper, we propose the use of discrete mixture distributions as a means 
of forecasting for projects similar to the CDC flu competition or the COVID-19
Forecast Hub. In section \ref{section:representations}, 
popular probabilistic forecast representation 
types are defined and reviewed. Methods of scoring, storing, building 
ensembles and other aspects will be reviewed and compared for each 
representation type.
In section \ref{section:conmixforc}, details for using discrete mixture 
distributions in a collaborative forecast project are presented as well as tools
which may be used for scoring and ensemble building.
Section \ref{section:retrostud} is a retrospective study of the CDC flu 
competition and COVID-19 
forecast predictions and an attempt to assess whether any predictions 
approximately come from well known continuous distributions. This paper is 
concluded with a discussion.

\section{Probabilistic Forecast Representations}
\label{section:representations}

Before introducing discrete mixture distributions as a representation type for a
probabilistic forecast, we review representations already commonplace in 
forecasting. In a collaborative setting, certain aspects of each representation
should be considered. With each representation presented, 
commmon applications of 
scoring, data storage and ensemble construction will be considered for
as well as other notable properties.

\subsection{Representation properties to consider in collaborative projects}
\subsubsection{Scoring}
Scoring rules are used to numerically evaluate or score a probability forecast. 
The
score is a measure of the accuracy of the forecast and where multiple forecasts
exist the score for each may be used to compare forecasts. If a scoring rule 
is proper, then the best possible score is obtained by reporting the true 
distribution. The rule is strictly proper if that value is unique. 
Under proper
scoring rules, a forecaster has no incentive to be dishonest in their 
submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
for evaluating forecasts. We will limit our review of scoring methods to rules
which are proper.

\subsubsection{Storage}
For a collaborative forecast project where many researchers are involved and 
many predictions are collected, computer storage may need to be addressed. 
As an example of required computer storage, the 
repository for the
COVID-19 Forecast Hub predictions contained 85 million predictions as of 
February 5, 2022 which required more than 11.6 gigabytes of storage!
(cite zoltar??)
When determining the goals of a forecast project, there should be consideration 
of the storage required for different forecast representation types.

\subsubsection{Ensemble Modeling}
A multi-model ensemble is a statistical model made by combining information from
two or more individual statistical models. Private and public decisions are 
regularly made after combining information from multiple sources. For any given
situation, information from one source may provide insight on a subject which 
other
sources fail to capture. Likewise one statistical model may provide insight
that another model does not, so that when they are combined in an ensemble the 
ensemble model outperforms the individual component models.

@@

\subsection{Probabilistic Forecast Representation Types}
\subsubsection{Parametric distributions}
\label{section:pardist}
A parametric distribution is a discrete or continuous probability distribution 
described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
pdf in the continuous case. Here $\theta$ is a vector of known or unkown 
parameters 
contained in a parameter space.

@@

\subsubsection{Sample Distributions}
Some forecast model builders may want more flexibility in modeling than a 
parametric 
distribution can provide. Methods that require sampling from a posterior 
distribution or Bootstrap sampling to obtain a sample distribution are examples
where parametric distributions may not be appropriate for modeling.

@@

\subsubsection{Discretized bin distributions}
An alternative to parametric distributions and sample distributions which allows
for higher flexibility in distribution shape than a parametric distribution and 
will usually require less storage space than samples is a discretized bin 
distribution.

@@

\subsubsection{Quantile representation}
When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
the time pressure of generating forecasts and the consideration of the large
range for possible outcomes both contributed to the COVID-19 Forecast Hub 
decision
to forego trying to create the right binning scheme and use sets of prediction
intervals to represent uncertainty in predictions \cite{bracher2021evaluating}.

@@

\subsection{Discrete mixture of parametric distributions}
A discrete mixture of parametric distributions forecast representation may be an
attractive alternative to the four types already discussed. A discrete mixture 
would allow for many distribution shapes, a high resolution, storage comparable
to that of discretized bins and quantile representations and the use of the more
common methods for scoring and ensemble building.

@@

\section{Mixture distributions in a collaborative forecast project}
\label{section:conmixforc}

The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
have their own established systems for receiving, 
evaluating and constructing ensemble forecasts. A transition from using binned 
distributions or quantile forecasts to using discrete mixture distributions 
nwould require
a few adjustments to those systems. In this section we outline how some of these
adjustments may be implemented as well as present some tools which may be used
to evaluate forecasts and construct ensemble forecasts from multiple models.

\subsection{Submission format}
For a collaborative forecast project to run smoothly, model submissions from all 
modelers should all follow the same format. For both the CDC flu forecasting and
the COVID-19 Forecast Hub, teams are provided a .csv spreadsheet with columns 
similar to those in tables \ref{table:dbins} and \ref{table:qstor}. Additionally
columns for Location, Target, Type and Unit are included which serve as
indicators of the specific prediction. The values for all variables except 
Value come from a specified list from the forecast center. Value is the 
probability assigned to a bin when the Type is Bin.

\begin{table}[h!]
\label{tab:dstan}
\centering
 \begin{tabular}{|c|c|c|c|c|c|}
 \hline
    Location & Target & Type & Unit & Bin & Value  \\ \hline
    US National & Season Onset & Point & week & NA & . \\
    US National & Season Onset & Bin & week & 0.0 & . \\
    US National & Season Onset & Bin & week & 0.1 & . \\
    ... & ... & ... & ... & ... & ... \\
 \hline
 \end{tabular}
 \caption[Influenza competition submission example]{Example of a submission file
 for an discretized forecast like those in the CDC influenza forecast 
 competition. To match a quantile submission format as used by
 the COVID-19 Forecast Hub, possible values for the variable Type are Point and
 Quantile, the Bin column is replaced with a Quantile column and Value is 
 the value of the specified quantile in the forecast.}
 \label{table:dstan}
\end{table}

For the quantile forecasts of the Forecast Hub, the main changes to table
\ref{tab:dstan} are that the possible values for Type 
are Point and Quantile, and rather than using a Bin variable Quantile is used
with values specified by the Hub. Then Value rather than a probability is the
forecasted value for the specified quantile. Per prediction there may be a 
couple dozen rows, up to 24 in the Forecast Hub, or over 100 rows as in some
flu forecasts.

In the discrete mixture format, an adjustment may be made to the format of table 
\ref{table:dstan} where each 
row
represents a component in a mixture distribution.
The variables Bin/Quantile and Value are removed and replaced with Family,
Param1, Param2 and Weight where Family is the distribution family,
Params are the parameters for the component distribution and Weight is the 
weight $w_i$ for that component.

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 \hline
    Location & Target & Type & Unit & Family & Param1 & Param2 & Weight
    \\ \hline
    US National & Season Onset & Dist & week & norm & $\mu_n$ & $\sigma_n$ & .\\
    US National & Season Onset & Dist & week & lnorm & $\mu_l$ & $\sigma_l$ &.\\
    ... & ... & ... & ... & ... & ... & ... & .\\
 \hline
 \end{tabular}
 \caption[Mixture distribution forecast submission example]{Example of a 
 submission file
 for a disease outbreak forecast using mixture distribution representation}
 \label{table:dstan}
\end{table}

@@

\subsection{Mixture construction and scoring tools}
\label{section:tools}

@@

\subsection{Ensemble construction}

@@

\section{Retrospective Analysis}
\label{section:retrostud}

@@

\subsection{CDC Influenza like Illness}
The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
850,000 probabilistic influenza-like illness predictions for all combinations
of eleven regions 
in the United States and seven targets from twenty-seven different models. These
include predictions during Influenza season between October 2010 and December
2018. All predictions are in the form of discretized probability bins.

@@

\subsection{COVID-19 Forecast Hub}

@@

\newpage

\section{Discussion}

@@

%\bibliographystyle{acm} % use for numbered citations along with options given in preamble. Look at the main thesis.tex file
\bibliographystyle{apa}
\bibliography{master_bib}

\section{Appendix}

@@

%\clearpage
%% \nocite{*}
%\unappendixtitle
%\newpage
%% % \phantomsection
%\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
%\section*{BIBLIOGRAPHY}
%\bibliographystyle{apa}
%\vspace{-20pt}
%\begingroup
%    \setlength{\bibsep}{14.5pt}
%    \linespread{1}\selectfont
    % \bibliography{master_bib}
%\endgroup

>>>>

\usepackage{framed}
\usepackage{changepage}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[svgnames]{xcolor}
\usepackage{graphicx}
\usepackage{subfig}
% Standard, old-style thesis
\usepackage{isutraditional}   
\chaptertitle
% Old-style, thesis numbering down to subsubsection
\alternate
% \nochap
\usepackage{rotating}
% Bibliography without numbers or labels
\usepackage{natbib}
% Use the following line if you want square brackets and numbering system
% \usepackage[square, numbers]{natbib}
% \lstset{language=R,
%     basicstyle=\small\ttfamily,
%     stringstyle=\color{DarkGreen},
%     otherkeywords={0,1,2,3,4,5,6,7,8,9},
%     morekeywords={TRUE,FALSE},
%     deletekeywords={data,frame,length,as,character},
%     keywordstyle=\color{blue},
%     commentstyle=\color{DarkGreen},
% }
\makeatletter

@@

\usepackage{chapterbib}
%\renewcommand\bibsection{\section*{\ref name}}
%\renewcommand\bibsection{\section*}
\renewcommand{\bibsection}{\section*{}}

@@

\usepackage{amssymb}
\usepackage[intoc, english]{nomencl}
\renewcommand{\chaptername}{}
\begin{document}
\SweaveOpts{concordance=TRUE}
\DeclareGraphicsExtensions{.jpg,.pdf,.mps,.png}
%\begin{singlespace}
\def\@makechapterheada{\vspace*{-2cm}\titlepage} % in order to reduce the space between margin and heading in titlepage
\include{Preface/titlepage}
%\end{singlespace}

@@

\chapter{Introduction}

Predicting the outcomes of prospective events is the object of much scientific
inquiry and the basis for many decisions both public and private. Because 
predictions of the future can almost never be precise, it is usually desirable
that a level of uncertainty be attached to any prediction. In recent years, it
has become increasingly desirable that forecasts be probabilistic in order to 
account for uncertainty in predicted quantities or events 
\cite{gneiting2014probabilistic}. Specific problems for 
which probabilistic forecasting is used include weather forecasting
\cite{baran2018combining}, economics \cite{groen2013real}, and disease outbreaks
\cite{yamana2016superensemble}.

A probabilistic forecast is a forecast to which probabilities are assigned to 
various possible outcomes. There are a number of ways whereby probabilities or 
uncertainty may be represented. A common representation is either a continuous 
or
discrete parametric distribution, given as a probability density/mass function 
(pdf/pmf). Much of the literature 
on calibration, sharpness, and scoring of a forecast pertains to parametric 
distribution forecasts
\cite{gneiting2007probabilistic,gneiting2013combining,baran2018combining}.
Other common representations include samples \cite{krueger2016probabilistic}, 
discretized bin distributions \cite{mcgowan2019collaborative},
and quantile forecasts \cite{taylor2021evaluating, bracher2021evaluating}. 
Each representation may be more or less 
appropriate than the others for a given problem but knowing how to interpret, 
score, and contruct ensemble forecasts for a selected representation is 
essential when multiple teams collaborate in the same forecasting project.

Two collaborative projects on forecasting disease outbreaks for which many 
separate forecasts 
are used include the United States Centers for Disease Control (CDC)
annual competition for forecasting the influenza outbreak \cite{cdcflusight}
and the COVID-19 Forecast Hub which has 
continuously operated since the start of the COVID-19 pandemic in the US in 
early 2020 \cite{Cramer2021-hub-dataset}.

\section{CDC flu competition}

Since the 2013-14 flu season, the CDC has hosted an annual competition for 
forecasting the timing, peak, and intensity of the year's flu 
season. The specific events to be forecasted are known as \emph{targets}.
Forecasts
for these different targets also include forecasts for one, two, three, and 
four weeks ahead of the prediction time. National flu data is provided weekly 
to academic teams not directly affiliated with the CDC who use that data to 
construct forecasts using 
whatever methods they choose. Historically, the forecasts must be 
submitted 
in a discretized bin distribution
format. A \emph{bin distribution} is a probability distribution represented by
breaking the numeric range of an event into intervals or \emph{bins} and
directly assigning the probability that the event falls within each bin.
During previous flu seasons the \emph{binning scheme} or the assignment of 
bin values was on a numeric 
scale with a bounded range and the 
prediction of a specific target was a set of probabilities assigned to each bin
\cite{mcgowan2019collaborative}.
These forecasts were then evaluated against actual flu activity, and at 
the end of the season a winning team was declared \cite{cdcflusight}.

This competition has provided the CDC, competing teams, and other interested
parties a chance to collaborate and improve their forecasting from season to
season. One 
proposed way to enhance prediction has been to aggregate the various teams'
forecasts into a \emph{multi-model ensemble forecast} 
\cite{mcgowan2019collaborative,mcandrew2019adaptively,reich2019accuracy},
refered to hereafter as an ensemble forecast.

An \emph{ensemble forecast} is a combination of several component forecast 
models into one model which often yields better predicting power than the 
individual models \cite{cramer2021evaluation}. Such an ensemble made from 
multiple influenza competition forecasts did in fact outperform the individual 
component models \cite{reich2019accuracy}.
In the COVID-19 Forecast Hub, construction of ensemble forecasts to improve
predicting power has been a priority.

\section{COVID-19 Forecast Hub}
In March 2020, at the onset of the COVID-19 pandemic, the COVID-19 Forecast Hub
was founded. Borrowing from the work done in the CDC flu competition, the 
COVID-19 Forecast Hub is a central site in 
which dozens of academic teams collaborate to forecast the ongoing COVID-19 
pandemic.
Every week relevant
pandemic data is provided to these teams who construct forecasts models to 
predict the targets cases, hospitalizations, and deaths due to COVID-19. 
Forecasts are 
made on the US county,
state, and national levels and for days, weeks, and months ahead.
These forecasts are aggregated into a single ensemble forecast. The model data,
forecasts, and the ensemble forecast are passed along to the CDC for its use in 
official
communication \cite{Cramer2021-hub-dataset}. See Figure \ref{fig:cdcoff}.

Though similar to the forecasting in the CDC flu competition, the format of 
the COVID-19 Forecast Hub has some key distinctions. For one this project has
been operating continuously since it first began, so forecasts have been made
for over 100 straight weeks. 
As well due to the initial lack of understanding of the COVID-19 virus and the 
time 
pressure of
creating forecasts, rather than requesting forecasts as bin distributions
the forecasts are requested as the predictive median and 
predictive intervals for various nominal levels depending on the target to be
predicted \cite{bracher2021evaluating}. Each value in a predictive interval
is a value for a quantile at a specified nominal level. This makes a set of 
predicitve intervals a \emph{quantile forecast} or a forecast made up of a set
of quantiles and corresponding values.
Collecting forecasts as quantile forecasts instead of bin forecasts brings with 
it differences in how to score, construct an 
ensemble forecast, and store the forecasts among other differences.

\begin{figure}[htbp]
\begin{center}
\begin{minipage}{10cm}
\captionsetup{font=scriptsize}
\centerline{\includegraphics[scale=.12]{Images/8_30_21_cvd_deaths.jpeg}}
\caption[Official CDC COVID-19 deaths report August 2021]{This image, 
published on www.cdc.gov in August 2021 as official public communication 
by the CDC, shows forecast models for national new weekly deaths due to COVID-19 
in the top row and cumulative deaths on the bottom row. The plots in the left 
column show prediction intervals from multiple teams whereas the plots on the 
right show the intervals for an ensemble forecast model.}
\label{fig:cdcoff}
\end{minipage}
\end{center}
\end{figure}

\section{Outline}
In the context of collaborative forecasting like that of the CDC flu competition
or the COVID-19 Forecast Hub, bin forecasts and quantile forecasts have become
important representations to those involved in the projects. Yet both 
representation types come 
with their drawbacks. Data 
storage for instance might be a concern if many bins are used for forecasting. 
And scoring methods are limited if forecasts are quantile forecasts.

In this paper, we propose the use of discrete mixture distributions as a means 
of forecasting for collaborative projects similar to the CDC flu competition or 
the COVID-19
Forecast Hub. In Section \ref{section:representations}, 
popular probabilistic forecast representation 
types are defined and reviewed. Methods of scoring, storing, constructing 
ensembles, and other aspects will be reviewed and compared for each 
representation type.
In Section \ref{section:conmixforc}, details for using discrete mixture 
distributions in a collaborative forecast project are presented as well as tools
which may be used for scoring and constructing an ensemble.
Section \ref{section:retrostud} is a retrospective study of the CDC flu 
competition and COVID-19 Forecast Hub
forecast and an attempt to assess whether any forecast models
may be approximated by known continuous distributions. We conclude this 
paper with a discussion.

\chapter{Probabilistic forecast representations}
\label{section:representations}

In this section we review four forecast representations already commonplace in 
forecasting. In a collaborative setting, certain aspects of each representation
should be considered including scoring, computer storage, and how to construct
an ensemble forecast. For each representation presented, applications of each of 
those aspects are also presented.

\section{Representation aspects to consider in collaborative projects}
\subsection{Scoring}
Scoring rules are used to numerically evaluate or score a probability forecast. 
The
score is a measure of the accuracy of the forecast and where multiple forecasts
exist the score for each may be used to compare forecasts. If a scoring rule 
is proper, then the best possible score is obtained by reporting the true 
distribution. The rule is strictly proper if that value is unique. 
Under proper
scoring rules, a forecaster has no incentive to be dishonest in their 
submission \cite{gneiting2007strictly}. This makes proper scoring rules ideal
for evaluating forecasts. We will limit our review of scoring methods to rules
which are proper.

\subsection{Storage}
For a collaborative forecast project where many researchers are involved and 
many predictions are collected, computer storage may need to be addressed. 
As an example of required computer storage, the 
repository for the
COVID-19 Forecast Hub predictions contained 85 million predictions as of 
February 5, 2022 which required more than 11.6 gigabytes of storage!
(cite zoltar??)
When determining the goals of a forecast project, there should be consideration 
of the storage required for different forecast representation types.

\subsection{Ensemble Modeling}
A multi-model ensemble is a statistical model made by combining information from
two or more individual statistical models. Private and public decisions are 
regularly made after combining information from multiple sources. For any given
situation, information from one source may provide insight on a subject which 
other
sources fail to capture. Likewise one statistical model may provide insight
that another model does not, so that when they are combined in an ensemble the 
ensemble model outperforms the individual component models.

@@

\section{Probabilistic Forecast Representation Types}
\subsection{Parametric distributions}
\label{section:pardist}
A parametric distribution is a discrete or continuous probability distribution 
described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
pdf in the continuous case. Here $\theta$ is a vector of known or unkown 
parameters 
contained in a parameter space.

@@

\subsection{Sample Distributions}
Some forecast model builders may want more flexibility in modeling than a 
parametric 
distribution can provide. Methods that require sampling from a posterior 
distribution or Bootstrap sampling to obtain a sample distribution are examples
where parametric distributions may not be appropriate for modeling.

@@

\subsection{Discretized bin distributions}
An alternative to parametric distributions and sample distributions which allows
for higher flexibility in distribution shape than a parametric distribution and 
will usually require less storage space than samples is a discretized bin 
distribution.

@@

\subsection{Quantile representation}
When deciding how forecasts should be represented in the COVID-19 Forecast Hub,
the time pressure of generating forecasts and the consideration of the large
range for possible outcomes both contributed to the COVID-19 Forecast Hub 
decision
to forego trying to create the right binning scheme and use sets of prediction
intervals to represent uncertainty in predictions \cite{bracher2021evaluating}.

@@

\section{Discrete mixture of parametric distributions}
A discrete mixture of parametric distributions forecast representation may be an
attractive alternative to the four types already discussed. A discrete mixture 
would allow for many distribution shapes, a high resolution, storage comparable
to that of discretized bins and quantile representations and the use of the more
common methods for scoring and ensemble building.

@@

\chapter{Mixture distributions in a collaborative forecast project}
\label{section:conmixforc}

The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
have their own established systems for receiving, 
scoring, and constructing ensemble forecasts. A transition from using bin or 
quantile forecasts to using mixture distribution forecasts
would require
a few adjustments to those systems. In this section we outline how some of these
adjustments may be implemented as well as present some tools which may be used
to score forecasts and construct ensembles from multiple models.

\section{Submission format}
For a collaborative forecast project to run smoothly, model submissions from all 
modelers should follow the same format. For both the CDC flu competition and
the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet with 
columns 
similar to those in tables \ref{table:dbins} and \ref{table:qstor}. Additionally
columns for \texttt{location}, \texttt{target}, \texttt{type}, and \texttt{unit} 
are included.
Here \texttt{location} defines the specific county, state, or country of the 
forecast. The \texttt{target} variable defines what is forecasted for example
season onset, deaths, hospitalizations, etc. The \texttt{type} variable defines
the type for the \texttt{value} variable, \texttt{bin} or \texttt{quantile}.
The \texttt{unit} variable defines the time frame of the forecast: week,
two weeks, four weeks, etc. And the \texttt{value} variable is a number that 
either gives probability for a bin or the value for a quantile. Table
\ref{table:dstan} show what a few rows of a forecast 
submission file for the CDC flu competition look like.
For the quantile forecasts of the Forecast Hub, the main changes to Table
\ref{table:dstan} are that the possible values for \texttt{type} 
quantile, and rather than using a \texttt{bin} variable \texttt{quantile} is 
used
with values specified by the Hub. This is seen in Table \ref{table:qstan}

A single submission may include many forecasts each aimed at predicting a 
different combination of \texttt{location}, \texttt{target}, and \texttt{unit}. 
A set of rows which share
the same specific combination of \texttt{location}, \texttt{target}, and 
\texttt{unit} constitute a single forecast. One forecast for the CDC flu
competition may require up to 131 rows whereas in the COVID-19 Forecast Hub one 
forecast may require up to 23 rows.

\begin{table}[h!]
\begin{center}
\begin{minipage}{10cm}
\captionsetup{font=scriptsize}
\centering
 \begin{tabular}{|c|c|c|c|c|c|}
 \hline
    location & target & type & unit & bin & value  \\ \hline
    % US National & Season Onset & Point & week & NA & . \\
    us national & season onset & bin & week & 0.0 & . \\
    us national & season onset & bin & week & 0.1 & . \\
    ... & ... & ... & ... & ... & ... \\
 \hline
 \end{tabular}
 \caption[Influenza competition submission example]{This shows a few rows of a 
 submission file
 for a discretized forecast like those in the CDC influenza forecast 
 competition. A set of rows which share the same combination of 
 \texttt{location}, \texttt{target}, and \texttt{unit} make up a
 single forecast. One submission may include many forecasts specified by 
 differing combinations of those three columns.}
 \label{table:dstan}
 \end{minipage}
 \end{center}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{minipage}{11cm}
\captionsetup{font=scriptsize}
\centering
 \begin{tabular}{|c|c|c|c|c|c|}
 \hline
    location & target & type & unit & quantile & value  \\ \hline
    % US National & Season Onset & Point & week & NA & . \\
    us national & season onset & quantile & week & 0.01 & . \\
    us national & season onset & quantile & week & 0.025 & . \\
    ... & ... & ... & ... & ... & ... \\
 \hline
 \end{tabular}
 \caption[COVID-19 Forecast Hub competition submission example]{This shows
 a few rows of a 
 submission file
 for a quantile forecast like those in the COVID-19 Forecast Hub. 
 A set of rows which share the same combination of 
 \texttt{location}, \texttt{target}, and \texttt{unit} make up a
 single forecast. One submission may include many forecasts specified by 
 differing combinations of those three columns.}
 \label{table:qstan}
 \end{minipage}
 \end{center}
\end{table}

In the mixture distribution format, an adjustment may be made to the format of 
Tables
\ref{table:dstan} and \ref{table:qstan} where each 
row
represents a component in a mixture distribution.
The variables Bin/Quantile and Value are removed and replaced with Family,
Param1, Param2 and Weight where Family is the distribution family,
Params are the parameters for the component distribution and Weight is the 
weight $w_i$ for that component.

\begin{table}[h!]
\centering
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 \hline
    location & target & type & unit & family & param1 & param2 & weight
    \\ \hline
    US National & Season Onset & Dist & week & norm & $\mu_n$ & $\sigma_n$ & .\\
    US National & Season Onset & Dist & week & lnorm & $\mu_l$ & $\sigma_l$ &.\\
    ... & ... & ... & ... & ... & ... & ... & .\\
 \hline
 \end{tabular}
 \caption[Mixture distribution forecast submission example]{Example of a 
 submission file
 for a disease outbreak forecast using mixture distribution representation}
 \label{table:mstan}
\end{table}

@@

\section{Mixture construction and scoring tools}
\label{section:tools}

@@

\section{Ensemble construction}

@@

\chapter{Retrospective Analysis}
\label{section:retrostud}

@@

\section{CDC Influenza like Illness}
The CDC Retrospective Forecasts project at zoltrdata.com (cite??) contains over
850,000 probabilistic influenza-like illness predictions for all combinations
of eleven regions 
in the United States and seven targets from twenty-seven different models. These
include predictions during Influenza season between October 2010 and December
2018. All predictions are in the form of discretized probability bins.

@@

\section{COVID-19 Forecast Hub}

@@

\chapter{Discussion}

@@

%\bibliographystyle{acm} % use for numbered citations along with options given in preamble. Look at the main thesis.tex file

% \bibliographystyle{apa}
% \bibliography{master_bib}

\clearpage
\nocite{*}
\unappendixtitle
\newpage
\phantomsection
\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}
\section*{BIBLIOGRAPHY}
\bibliographystyle{apa}
\vspace{-20pt}
\begingroup
   \setlength{\bibsep}{14.5pt}
   \linespread{1}\selectfont
\bibliography{master_bib}
\endgroup

\appendix

\specialchapt{APPENDIX}

@@
